\documentclass[10pt, a4paper]{article}
\usepackage[margin=2.5cm]{geometry} % Sets all margins to 2.5cm
\usepackage[T1]{fontenc}
\usepackage[normalem]{ulem}
\usepackage{soul}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{makecell}
\definecolor{Light}{gray}{.90}
\sethlcolor{Light}
\usepackage{fontawesome}
\usepackage{tcolorbox}
\usepackage{url}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{tikz}

\newcommand{\circnum}[1]{%
  \tikz[baseline=(char.base)]{
    \node[draw,circle,inner sep=1pt] (char) {#1};
  }%
}
\newcounter{descriptcount}
\newlist{enumdescript}{description}{2}
\setlist[enumdescript,1]{%
  before={\setcounter{descriptcount}{0}%
          \renewcommand*\thedescriptcount{\arabic{descriptcount}}}
  ,font=\bfseries\stepcounter{descriptcount}\circnum{\arabic{descriptcount}}~
}
% 2nd level
\setlist[enumdescript,2]{%
  before={\setcounter{descriptcount}{0}%
          \renewcommand*\thedescriptcount{\roman{descriptcount}}}
  ,font=\bfseries\stepcounter{descriptcount}\thedescriptcount~
}


% \renewcommand{\texttt}{\hl}
\newcommand{\code}[1]{\texttt{\hl{#1}}}

\newcommand{\genericbox}[4]{%
\footnotesize
\begin{tcolorbox}[width=.95\textwidth,colback={#1},title={#3},colbacktitle={#2},coltitle=black]
#4
\end{tcolorbox}
\normalsize
}
\newcommand{\examplesbox}[1]{%
\genericbox{blue!10!white}{blue!30!white}{\faHandORight\ Examples}{#1}
}
\newcommand{\protipbox}[1]{%
\genericbox{yellow!10!white}{yellow!30!white}{\faLightbulbO\ Pro Tip}{#1}
}
\newcommand{\exampleFalse}{%
    \textcolor{red}{\faClose}
}
\newcommand{\exampleCorrect}{%
    \textcolor{blue}{\faCheck}
}

\title{Frequent Errors in Scientific Writing}
\author{Stefan Lengauer}
\date{Version 0.2, \today}

\begin{document}

\maketitle


\noindent This checklist constitutes a list of bad practices I encounter in almost every Seminar Paper, Bachelor/Master thesis, or research paper I had the pleasure to review\footnote{
\uline{Disclaimer:} the outlined points reflect both established best-practices and (in some cases) my personal preferences and recommendations. As the latter are subjective, feel free to respectfully disagree.}\footnote{Footnotes should generally be avoided in scientific writing.}. 
For most I provide strategies on how they can be avoided. 
Some of them are specific to the usage of \LaTeX\ while others are general recommendations. 
%
%
If you want to have targeted feedback, please make sure that your submitted work is reasonably free of these errors. 
% Please make sure that none of these errors appear in your work if you want to have feedback. 

\begin{enumdescript}
    \item [Usage of Acronyms] Acronyms should be introduced upon their first usage with the expanded version followed by the abbreviated version in brackets. 
        \begin{itemize}
            \item Do \underline{not} re-introduced already existing acronyms.
            \item If a concept is abbreviated, introduce the acronym on the first usage. 
            \item Once introduced, do \underline{not} use the expanded form. 
        \end{itemize}
    If \LaTeX is used, I heavily recommend to use the \code{glossaries} package. With that acronyms can be simply define with a handle: \\\code{\textbackslash newacronym\{handle\}\{abbreviation\}\{long form\}}. In text the expansion is handled automatically by just using \code{\textbackslash gls\{handle\}}. 
    For automatically handling pluralization, the package also supports a plural version: \code{\textbackslash glspl}. Yet, as this na\:ively appends an `s' to form the plural, the plural form for terms ending with an `s' (e.g., Histogram of Oriented Gradients) must be set explicitly through the flags \code{shortplural}/\code{longplural}.
    Use \code{\textbackslash glsdisablehyper} to prevent \LaTeX\ from inserting hyperlinks for every acronym.

    \protipbox{Sometimes an acronym is used only a single time. In such cases \uline{omitting} the abbreviated form can reduce the text's complexity and improve readability. 
    The \code{glossaries} package provides a setting for counting the usage of acronyms, which can be set with \code{\textbackslash glsenableentrycount}. In conjunction with \code{\textbackslash cgls} this can be used to automate this behavior. 
    }  
    
    \item [Smart Quotes] For the \LaTeX\ compiler to render quotes correctly (i.e., opening/closing quotes), \code{\textasciigrave} and \code{\textquotesingle} and \code{\textasciigrave\textasciigrave} or \code{\textquotesingle \textquotesingle} must be used for single- and double quotes respectively. Do \underline{not} use \code{"}!
    \examplesbox{
       \begin{tabularx}{\textwidth}{p{4mm}@{}X|p{4mm}@{}X}
           \exampleFalse & "Some relevant quote" 
           & \exampleCorrect & ``Some relevant quote'' \\
       \end{tabularx}
    }   
    \item [Language] ~
        \begin{description}
            \item[Consistency] Do not mix US and UK English. E.g., color vs. colour or visualization vs. visualisation. 

            When referring to completed work either singular (``I'', ``my'') or plural form (``we'', ``our'') can be used, but this should remain consistent throughout the document.
            \item[Tenses]
            Do not switch between tenses. 
            I recommend to stick to present tense (even for related work). 
            If using past tense cannot be avoided for some reason, make sure that it is consistent within the respective paragraph.
            \item[Stringency] Avoid using conjunctive forms such as ``may'', ``might'', ``could'', ``should'', but use self-assured formulations such as ``My solution demonstrates/supports xy''. 
            Also, avoid imprecise quantifications such as ``somewhat'', or ``a little''.
            \item[Informality] Do not use informal language such as ``it's'' or ``they're''.
        \end{description}
    \examplesbox{
       \begin{tabularx}{\textwidth}{p{4mm}@{}X|p{4mm}@{}X}
           \exampleFalse & It's, they're, can't.
           & \exampleCorrect & It is, they are, cannot. \\
       \end{tabularx}
    }    
        
    \item [Captions] Captions should be full sentences and end with a dot. They should fully describe the respective figure/table such that the element can be understood without the floating text. 
    For tables, listings, and algorithms the caption should be \uline{on top}.
    \protipbox{If a list of figures, list of tables is printed, a short version of the caption can also be provided as optional parameter \code{\textbackslash caption[short caption]\{full caption\}}, which is used there.
    }
    \item [Equations] Equations are part of a sentence, even if they are written in ``display'' math mode. 
    When referencing an equation, \code{\textbackslash eqnref} must be used (renders the number in brackets). 
    \examplesbox{
       \begin{tabularx}{\textwidth}{p{4mm}@{}X|p{4mm}@{}X}
           \exampleFalse 
           & We define $y$ in Eqn.~\eqref{eq:test}.
           \begin{equation} \label{eq:test}
            y = x + k
            \end{equation}
           & \exampleCorrect 
           & We define $y$ as 
           \begin{equation} 
            y = x + k \text{,}
            \end{equation}
            where $x$ is [\dots]  \\ 
           && \exampleCorrect & We define $y = x + k$, where $x$ is [\dots]
       \end{tabularx}
    }
    \protipbox{
        When an equation is never referenced in the text, the auto numbering can suppressed by using the `*' versions of the respective environments. I.e., \code{\textbackslash equation*}, \code{\textbackslash align*}, \dots
    }
    \item [References] When referring to a concrete figure, table, equation (e.g., see Figure~1), use uppercase Figure, Table, Equation (or Fig., Tab., Eqn.). Use a non-breaking space (NBS) \code{\textasciitilde} to avoid line breaks between the label and the reference number. 
    Do \uline{not} use merely numbers as reference. 
    \examplesbox{
       \begin{tabularx}{\textwidth}{p{4mm}@{}X|p{4mm}@{}X}
           \exampleFalse & as shown in 2. 
           & \exampleCorrect & as shown in Fig.~2. \\
           \exampleFalse & as in figure~1 & \exampleCorrect & as in Figure~1 \\ 
           \exampleFalse & see Eqn. 3. & \exampleCorrect & see Eqn. (3). \\ 
       \end{tabularx}
    }   
    
    \item [Citations] Citations must be part of the sentence -- i.e., if the citation if removed the sentence should still be valid. When the citation is used as a noun, write the author name(s) followed by the corresponding \code{\textbackslash cite}. 
    If the cited item has one or two authors write their last names, followed by the corresponding \code{\textbackslash cite}. 
    In case of more authors the last name of the first author followed by ``et al.'' is used. 
    If multiple citations are used together, put them in a single \code{\textbackslash cite}.
    If the authors' are referred to by name, the \code{\textbackslash cite} should be directly after, otherwise it can be at the end of the sentence/paragraph.

    If multiple consecutive sentences rely on information from a specific source, it is sufficient to cite it \uline{once}, either at the start or the end of this sequence.
    \examplesbox{
       \begin{tabularx}{\textwidth}{p{4mm}@{}X|p{4mm}@{}X}
           \exampleFalse 
           & Statement from reference. [1]
           & \exampleCorrect 
           & Statement from reference [1]. \\
           \exampleFalse
           & As shown by [1], we can [\dots]
           & \exampleCorrect
           & As shown by Someone et al.~[1], we can [\dots] \\
          \exampleFalse 
           & As presented by Pop, Asheton, and Alexander [1] \dots].
           & \exampleCorrect 
           & As presented by Pop et al.~[1] [\dots] \\
           \exampleFalse 
           & Various Statements [1][3][4][5][7]. & \exampleCorrect 
           & Various Statements [1,3-5,7]. \\ 
       \end{tabularx}
    }
    \protipbox{Some items take up comprehensive space in the references list. Even though it is essential that a reference contains all relevant items, there a several legit ways to reduce their extent:
    \begin{itemize}
        \item If a publication has more than 5 authors the list of names can be shortened with ``et al.''. With \code{biblatex} this can be governed through setting \code{maxbibnames}.
        % , for \code{bibtex} the authors for an bibentry can be manually shortened by writing \code{and others} instead of the 6th author. \textcolor{red}{CHECK}
        \item Editors can be omitted for technical papers. 
        \item If possible provide a DOI. Many applications which generate entries, generate URLs alongside the DOIs, which is then just the DOI prefixed with \url{https://doi.org/}. In cases where a DOI exists, this URL can be omitted.
    \end{itemize}
    }
    \item [Enumerations/Bullet Lists] In English bullet points start with an \uline{uppercase} letter. 
    The should form a valid sentence -- i.e., with a comma after each point and a dot at the end. 
\end{enumdescript}
\end{document}
